---
title: "Using Quarto (R) For Creating Interactive Presentations"
subtitle: "<span style='color: #AD192E;'>Echarts4r is used for interactive plots</span>"
author: 'Oliver Zingg'
format: 
  revealjs: 
    slideNumber: true
    theme: 
      - simple
    embed-resources: true
    controls: true

    
---

```{r}
#| include: false # dont include this code cell into presentation
library(tidyverse) #package for data wrangling
library(echarts4r) #package for creating interacting charts
library(gt) #package for creating tables 




```
# Table Of Contents{.sb-turkis-red}
- How to navigate this presentation
- First Plot
- ....



# How to Navigate This Presentation {background-color="#AD192E"}

## How to Navigate This Presentation{.sb-turkis-red}

:::{.incremental .highlight-last}
- Click on the presentation to active the window and press *F* for full screen
- With *ESC* full screen is exited.
- Use arrow keys or space to go back and forth
:::


# First Plot{background-color="#19ad98"}

##


```{r}
library(palmerpenguins)
library(RColorBrewer)

penguins <- palmerpenguins::penguins

my_colors <- brewer.pal(3, "Dark2")

penguins |>
  group_by(species) |>
  e_charts(bill_length_mm) |>
  e_scatter(flipper_length_mm, symbol_size = 7) |>
  e_title('Comparing Three different Penguins Species', 
          subtext = 'Flipper Length (mm) vs Bill Length (mm)') |>
  e_lm(flipper_length_mm ~ bill_length_mm)|>
  e_legend(
    orient = 'vertical',
    right = '5%',
    top = '40%') |>
  e_y_axis(min = 160, max = 250) |>
  e_x_axis(min = 30) |>
  e_color(my_colors) |>
  e_grid(right = '20%') |>
  e_tooltip(trigger = "axis") |>
  e_toolbox_feature('saveAsImage') |>
  e_toolbox_feature('dataView') 


```


# Code First Plot {background-color="#AD192E"}

## Load Packages

```{r}
#| echo: TRUE
#| eval: FALSE
#| code-line-numbers: "1-2"
library(palmerpenguins)
library(RColorBrewer)

penguins <- palmerpenguins::penguins

my_colors <- brewer.pal(3, "Dark2")

penguins |>
  group_by(species) |>
  e_charts(bill_length_mm) |>
  e_scatter(flipper_length_mm, symbol_size = 7) |>
  e_title('Comparing Three different Penguins Species', 
          subtext = 'Flipper Length (mm) vs Bill Length (mm)') |>
  e_legend(
    orient = 'vertical',
    right = '5%',
    top = '40%') |>
  e_y_axis(min = 160, max = 250) |>
  e_x_axis(min = 30) |>
  e_color(my_colors) |>
  e_grid(right = '15%') |>
  e_tooltip(trigger = "axis") |>
  e_toolbox_feature('saveAsImage') |>
  e_toolbox_feature('dataView')
  

```



## Load Data

```{r}
#| echo: TRUE
#| eval: FALSE
#| code-line-numbers: "4"
library(palmerpenguins)
library(RColorBrewer)

penguins <- palmerpenguins::penguins

my_colors <- brewer.pal(3, "Dark2")

penguins |>
  group_by(species) |>
  e_charts(bill_length_mm) |>
  e_scatter(flipper_length_mm, symbol_size = 7) |>
  e_title('Comparing Three different Penguins Species', 
          subtext = 'Flipper Length (mm) vs Bill Length (mm)') |>
  e_legend(
    orient = 'vertical',
    right = '5%',
    top = '40%') |>
  e_y_axis(min = 160, max = 250) |>
  e_x_axis(min = 30) |>
  e_color(my_colors) |>
  e_grid(right = '15%') |>
  e_tooltip(trigger = "axis") |>
  e_toolbox_feature('saveAsImage') |>
  e_toolbox_feature('dataView')
  

```

## Load Colors

```{r}
#| echo: TRUE
#| eval: FALSE
#| code-line-numbers: "6"
library(palmerpenguins)
library(RColorBrewer)

penguins <- palmerpenguins::penguins

my_colors <- brewer.pal(3, "Dark2")

penguins |>
  group_by(species) |>
  e_charts(bill_length_mm) |>
  e_scatter(flipper_length_mm, symbol_size = 7) |>
  e_title('Comparing Three different Penguins Species', 
          subtext = 'Flipper Length (mm) vs Bill Length (mm)') |>
  e_legend(
    orient = 'vertical',
    right = '5%',
    top = '40%') |>
  e_y_axis(min = 160, max = 250) |>
  e_x_axis(min = 30) |>
  e_color(my_colors) |>
  e_grid(right = '15%') |>
  e_tooltip(trigger = "axis") |>
  e_toolbox_feature('saveAsImage') |>
  e_toolbox_feature('dataView')
  

```


## Creat Interactive Plot

```{r}
#| echo: TRUE
#| eval: FALSE
#| code-line-numbers: "8-24"
library(palmerpenguins)
library(RColorBrewer)

penguins <- palmerpenguins::penguins

my_colors <- brewer.pal(3, "Dark2")

penguins |>
  group_by(species) |>
  e_charts(bill_length_mm) |>
  e_scatter(flipper_length_mm, symbol_size = 7) |>
  e_title('Comparing Three different Penguins Species', 
          subtext = 'Flipper Length (mm) vs Bill Length (mm)') |>
  e_legend(
    orient = 'vertical',
    right = '5%',
    top = '40%') |>
  e_y_axis(min = 160, max = 250) |>
  e_x_axis(min = 30) |>
  e_color(my_colors) |>
  e_grid(right = '15%') |>
  e_tooltip(trigger = "axis") |>
  e_toolbox_feature('saveAsImage') |>
  e_toolbox_feature('dataView')
  

```


